\documentclass[a4paper,11pt]{article}
\usepackage[top=0.2in, bottom=0.2in, left=0.75in, right=0.75in]{geometry}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{graphicx}

% Define colors
\definecolor{darkblue}{RGB}{0, 78, 102}
\definecolor{graytext}{RGB}{80, 80, 80}

% new rule for hrule after section title
\newcommand{\hruleafter}[1]{#1\hrule}
% Section formatting
\titleformat{\section}{\large\bfseries\color{darkblue}}{}{0em}{\hruleafter}
% Section spacing -- keep all at zero for most compact
\titlespacing*{\section}{0em}{0em}{0em}
% set font 
\renewcommand{\familydefault}{\sfdefault}
% disable page numbers
\pagenumbering{gobble}

\begin{document}

% Top Level Header
\begin{center}
    {\LARGE \color{darkblue} \textbf{Hayden Haddock}} \\
    \vspace{1em}
    {\color{graytext}\textbf{Phone:} (314) 518 9870 \quad \textbf{Email:} \href{mailto:haydenhaddock1@gmail.com}{haydenhaddock1@gmail.com}} \quad
    {\color{graytext}\textbf{GitHub:} \href{http://github.com/hhaddock}{github.com/hhaddock}}
\end{center}

\section*{Education}
\noindent\textbf{University of Missouri \hfill Columbia, Missouri} \\
\quad B.S., Information Technology Engineering, Minor in Computer Science \hfill \textit{ 2015--2019}\\
\textbf{Relevant Coursework:} Software Engineering, Algorithm Design, Cyber Security, Database Systems, Full Stack Web Development, Object Oriented Programming

\vspace{1em}
\section*{Professional Experience}
\noindent \textbf{Mastercard Int.}\\
{\color{darkblue}\textit{Senior Software Engineer}} \hfill {\color{graytext}\textit{March 2023 -- Present}}
\begin{itemize}[leftmargin=2em,noitemsep]
    \setlength\itemsep{0em}
    \item Aided in MPGS modernization by contributing to \textbf{Spring Boot API} and \textbf{React} micro front-end development.
    \item Worked with stakeholders during Critical Security Events to \textbf{triage production issues} and implement resolutions.
    \item Mentoring for Junior engineers inside and outside of team. Provided guidance on technical skills development, gave suggestions on navigating the early career, and provided anecdotes about personal work experience.
    \item Led effort to upgrade core API integration with Mastercard Gateway to a significantly newer version encompassing several major architectural changes.
    \item Contributed to analysis, architectural discussions, and POC implementations for re-writing the Simplify Commerce platform using \textbf{Java} with \textbf{Spring Boot}.
\end{itemize}

\noindent \textbf{Mastercard Int.}\\
{\color{darkblue}\textit{Software Engineer II}} \hfill {\color{graytext}\textit{March 2022 -- March 2023}}
\begin{itemize}[leftmargin=2em,noitemsep]
    \item Created end-to-end implementation for new payment enhancement between Simplify Commerce platform and Mastercard Payment Gateway.
    \item Implemented three new languages on platform for \textbf{Angular} and \textbf{Grails} applications. Owned translation updates on platform.
\end{itemize}

\noindent \textbf{Mastercard Int.}\\
{\color{darkblue}\textit{Software Engineer I}} \hfill {\color{graytext}\textit{March 2020 -- March 2022}}
\begin{itemize}[leftmargin=2em,noitemsep]
    \item Worked with senior team members to re-write \textbf{AngularJS} application in modern \textbf{Angular} while simultaneously updating relevant dependencies and libraries.
    \item Extended developer \textbf{Command Line Interface} to incorporate new tools and simplify the onboarding process for new developers.
\end{itemize}

\section*{Projects}
\noindent \textbf{Web Service API Integration -- Version Upgrade} \hfill {\color{graytext}\textit{Mastercard - 2024}}
\begin{itemize}[leftmargin=2em,noitemsep]
    \item Led effort to update core API integration of the Simplify Commerce Product to significantly newer version.
    \item Worked with stakeholders to elaborate feature requirements, provide updates on development progress, and ensure proper sign-off after completion.
    \item Collaborated with Penetration Testing team to facilitate testing of all effected micro services before release into production.
\end{itemize}

\noindent \textbf{Platform Localization} \hfill {\color{graytext}\textit{Mastercard - 2022}}
\begin{itemize}[leftmargin=2em,noitemsep]
    \item Owned the implementation of three new languages on Simplify Commerce platform consisting of both Angular applications and REST API services written in Grails.
    \item Worked across team boundaries to ensure that new features were localized in all languages before their release in production and implemented any necessary changes to current translations.
\end{itemize}

\section*{Technical Skills}
\noindent \textbf{Programming Languages:} Java, JavaScript/jQuery, Groovy, TypeScript, SQL, HTML, CSS, \\
\textbf{Technology:} Spring Boot, Spring Web, Spring Security, Angular, React, NodeJS, PostgreSQL, Redis, Pivotal Cloud Foundry, Splunk, Jenkins, Git, Unix

\end{document}
